---
title: "Animate Your Science Visual Storytelling Workshop"
subtitle: "Evaluation (November 2023)"
# author: "Jen Beaudry"
# date: "2024-02-09"
output: pdf_document
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{caption}
  - \usepackage{titling}
    \setlength{\droptitle}{-2cm} # removes some of the white space above title
  - \pretitle{\begin{center}
    \includegraphics[width=1.5in, height=1.5in]{flinders-university-horizontal-master.png}\LARGE\\} # adds logo
  - \posttitle{\end{center}}
  - \usepackage{fancyhdr}
  - \fancypagestyle{plain}{\pagestyle{fancy}} # sets the footer on page 1
  - \pagestyle{fancy} # sets the footer on page 2 and beyond
  - \fancyhf{} # clears existing header & footer
  - \renewcommand{\headrulewidth}{0pt} # removes the line from the header
  - \fancyfoot[L]{Jen Beaudry} # my name in footer
  - \fancyfoot[R]{\thepage} # page number in foooter
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      include = TRUE, 
                      eval = TRUE)

```

```{r library, include=FALSE}

# devtools::install_github("adletaw/captioner")

library(here)
library(tidyverse)
library(kableExtra)
library(RColorBrewer)
library(captioner)

```

```{r functions, include=FALSE}

styler_pdf <- function(dat) {
  dat %>%
     kable_styling(full_width = F, 
                latex_options = c("striped", "HOLD_position"))
}

source(here("..", "functions", "meta_rename.R"))
source(here("..", "functions", "ratings_summary.R"))

table_nums <- captioner(prefix = "Table")
fig_nums <- captioner(prefix = "Figure")

```

```{r load data, include=FALSE}

df <- read_csv(here::here("data", "sci_comm_processed_data.csv"), lazy = FALSE)

```

```{r code factors, include=FALSE}


# turn all ratings variables into factors, use datapasta to do this!
# the code below works

df$expectations <- factor(df$expectations, levels = c("Exceeded my expectations", "Met my expectations", "Partly met my expectations", "Did not meet my expectations"))
df$follow_up <- factor(df$follow_up)

# work with all rating items together because they have the same levels

cols <- c(
  "understanding",
  "expert",
  "engaging",
  "balance",
  "storytelling",
  "reengagement")


# turn the cols columns into factors
df <- df %>% 
  mutate(across (all_of(cols), ~factor(., 
                                       levels = c("N/A", 
                                           "Strongly disagree",
                                           "Somewhat disagree",
                                           "Neither agree nor disagree",
                                           "Somewhat agree",
                                           "Strongly agree"))))

```

```{r captions, include = FALSE}

table_nums(name = "info_workshop", 
           caption = "'What did you expect from this workshop?'")

table_nums(name = "expectations", 
           caption = "'Please elaborate on how the workshop aligned with your expectations.'")

table_nums(name = "action", 
          caption = "'Did this workshop inspire you to take any immediate action(s)?'")

table_nums(name = "best_parts",
             caption = "'What were the best parts of the workshop?'")

table_nums(name = "improvement",
             caption = "'Any suggestions for improvement?'")

table_nums(name = "anything_else",
             caption = "'Anything else you want us to know?'")

fig_nums(name = "ratings_summary", 
         caption = "Ratings of different aspects of the workshop")

```



```{r sessions attendance}

participants <- 30

#breadcrumb for caption: \captionsetup[table]{labelformat=empty}
# that's if I include header use caption in the yaml

```


Dr Tullio Rossi from Animate your Science designed and delivered the 
*Visual Storytelling* workshop. This workshop was offered to our research community
for the first time in October 2023; the workshop was capped at 30 participants. 
Of the `r participants` participants in the workshop, `r nrow(df)` completed this evaluation.

We asked participants to rate a number of items about the workshop and the trainer 
on a scale from 'strongly disagree' to 'strongly agree' (see 
`r fig_nums(name = "ratings_summary", display = "cite")`).

\
`r fig_nums(name = "ratings_summary")`

```{r creating tibbles for all ratings, include = FALSE}

# get total n to calculate percentages

total_n <- length(df$id)

# SELECT THE RATING COLUMNS & SAVE AS A TIBBLE I WANT TO SUMMARISE & PLOT USING THE RATING_SUMMARY FUNCTION

ratings <- df %>% 
  select(c(
  "understanding",
  "expert",
  "engaging",
  "balance",
  "storytelling",
  "reengagement"))

# UPDATE THE COLUMNS PARAMETER WITH THE STRINGS FROM ABOVE

columns <- cols <- c(
  "understanding",
  "expert",
  "engaging",
  "balance",
  "storytelling",
  "reengagement")

# RUN THE FUNCTION & APPLY TO ALL COLUMNS IN OUR DF

ratings_summary <- purrr::map_dfr(columns, .f = function(column) {
	ratings_summary(ratings, column)
})

# remove the NA responses
ratings_summary <- na.omit(ratings_summary)


# also, figure out how many responded with the agree ratings. I use these in the 
  # text summaries later

# [breadcrumb: can I use apply for this too?? need to do this later!]

agree <- c("Strongly agree", "Somewhat agree")


```

```{r plot the ratings}

# Relevel the responses [changes order in ggplot, but not the dataframe]
# plot it first to see if I need to do this

# tor_rating$rating <- factor (rating$rating, levels = c("Strongly agree",
#                                            "Somewhat agree",
#                                            "Neither agree nor disagree",
#                                            "Somewhat disagree",
#                                            "Strongly disagree"))

# put them in reverse order of how I want them to appear
ratings_summary$rating_item <-
  factor (
    ratings_summary$rating_item,
    levels = c(
  "reengagement",
  "expert",
  "engaging",
  "balance",
  "storytelling",
  "understanding"
)
    )

# [breadcrumb] I can delete this later, but this is useful to create the plot_labs

# labs <- meta %>%
#   filter(scale == "common_ratings") %>%
#   pull(item_text_short) %>%
# datapasta::vector_paste_vertical()


# plot it


ggplot(ratings_summary, aes(fill = rating, y = percentage, x = rating_item)) +
  geom_bar(position="fill", stat="identity", colour = "black") +
  scale_fill_brewer(
    palette = "Blues",
    na.value = "grey50",
    direction = 1,
    labels = c(
      "N/A",
      "Strongly disagree",
      "Somewhat disagree",
      "Neither agree nor disagree",
      "Somewhat agree",
      "Strongly agree"
    )
  ) +
  labs (x = element_blank(),
        y = "Percentage") +
  theme_classic() +
theme(legend.title = element_blank()) +
    coord_flip() +
  scale_x_discrete(
    labels = c(
      "I would attend another workshop \nfrom this trainer",
           "The trainer is an expert in \nthe sector",
      "The trainer was very engaging",
      "The workshop had a good balance \nof working time and presentation",
      "The workshop provided valuable \ninsights about storytelling",
       "The workshop provided me with \na greater understanding of how to \nshare my research through videos"
 )
) +
  scale_y_continuous(labels = c("0", "25", "50", "75", "100"))

# FYI: the labels are always in opposite directions from the data set! Is it? I think they changed it!

```

\newpage

```{r expectations data, include = TRUE}

expect <- df %>% 
    dplyr::group_by (expectations) %>% 
  count()

```



All respondents indicated that the program met or exceeded their expectations. 
Of the `r nrow(df)` respondents, `r round((expect[1,2]/nrow(df))*100,2)`% indicated 
that it exceeded their expectations. 

`r table_nums("info_workshop", display = "cite")` reports what the respondents
said they expected from the workshop. Their explanations of how the program aligned with their expectations are shown 
in `r table_nums("expectations", display = "cite")`. 

\vskip 0.3in

```{r info_workshop table, include = TRUE}

info_workshop <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, info_workshop) %>% 
  filter (!is.na(info_workshop))


kable(
  info_workshop,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'What did you expect from this workshop?'",
  col.names = c("Participant", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```

\vskip 0.3in

```{r expectations table, include = TRUE}

expectations <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, expect_comment) %>% 
  filter (!is.na(expect_comment))


kable(
  expectations,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Please elaborate on how the workshop aligned with your expectations.'",
  col.names = c("Participant", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```


```{r follow_up data, include = TRUE}

follow <- df %>% 
    dplyr::group_by (follow_up) %>% 
  count()

```


We also asked if they would be interested in attending a follow-up session, 
which Tullio offers to give participants an opportunity to put their new skills 
into practice. After creating their video, they would receive feedback from 
Tullio and the group about what they did well and what they could do to improve
their storytelling.

Most respondents (`r round((follow[2,2]/nrow(df))*100,2)`%)
indicated that they would like the opportunity to attend a follow
up session.

We also asked them some open-ended questions about whether this workshop 
inspired them to take immediate action, what the best parts of the workshop
were, their suggestions for improvement, and anything else that we would like 
them to know. Their responses are presented in the following tables. 

```{r action table, include = TRUE}

action <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, actions) %>% 
  filter (!is.na(actions))


kable(
  action,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Did this workshop inspire you to take any immediate action(s)?'",
  col.names = c("Participant", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```

\vskip 0.3in

```{r best_parts table, include = TRUE}

best <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, best_parts) %>% 
  filter (!is.na(best_parts))

kable(
  best,
    booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'What were the best parts of the workshop?'",
  col.names = c("Participant", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```

\vskip 0.3in

```{r improvement table, include = TRUE}

improve <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, improvement) %>% 
  filter (!is.na(improvement))


kable(
  improve,
    booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Any suggestions for improvement?'",
  col.names = c("Participant", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```

\vskip 0.3in

```{r anything else table, include = TRUE}

anything_else <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, anything_else) %>% 
  filter (!is.na(anything_else))


kable(
  anything_else,
    booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Anything else you want us to know?'",
  col.names = c("Participant", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))


```

If you have any questions, please contact [Dr Jen Beaudry](mailto:jen.beaudry@flinders.edu.au) 
(Manager, Researcher Training, Development and Communication) in Research 
Development and Support. 
